PACE 2024: OCMu64, reductions and a branch-and-bound solver for\\ One-sided Crossing Minimization

### 2024-09-01 tex/poster.tex
perf
Insert figures

      \begin{alertblock}{todo}
        Figures.
      \end{alertblock}

@@

        \heading{Definitions}
        We use $<$ to compare vertices in $A$ in their fixed ordering.

        For $u\in B$, we write $N(u) \subseteq A$ for the set of its neighbours.

@@

        We write $u\b v$ when $u$ must come before $v$ in \emph{all} minimal solutions, and say that $(u, v)$
        is a \textbf{fixed pair}.

        A well known result is that when all neighbours of $u$ come before all
        neighbours of $v$, then $u\b v$.

        We try to fix as many pairs as possible to speed up the search.
      \end{block}

@@

        \textbf{The lamma is optimal:}
        Suppose that $u, v \in B$ with $N(u) \neq N(v)$ are not strongly fixed, and let $i$ be
        such that $b:=N(u)_i > N(v)_{\lfloor i\cdot m/n\rfloor}=:a$.
        Assuming there exists vertices $m$ in between $a$ and $b$, $l$ left of $\min
        N(v)$ and $r$ right of $\max N(u)$ \ragnar{Is this strong enough? Do $u$ and $v$
          need reversing? Or should we just say left of the min and right of the max
          of the two?}, there exists some \emph{weighted} distribution $X$ over
        $\{l, m, r\}$ such that $c(v, X, u) < \min(c(X, u, v), c(u, v, X))$, so that
        $v$ may have to go before $u$.
      \end{block}

@@

    \end{column}

@@

@@

      \begin{block}{Performance}

>>>>

@@

        We use $<$ to compare vertices in $A$ in their fixed ordering.
        For $u\in B$, we write $N(u) \subseteq A$ for the set of its neighbours.

@@

        We write $u\b v$ when $u$ must come before $v$ in \emph{all} minimal solutions, and say that $(u, v)$
        is a \textbf{fixed pair}.
        We try to fix as many pairs as possible to speed up the search.
        A well known result is that when $\max N(u) < \min N(v)$, then $u\b v$.

        \vspace{-1em}
        \centering
        \includegraphics[scale=2]{fig/simple.pdf}
      \end{block}

@@

        \textbf{The lamma is optimal:}
        Suppose that $u, v \in B$ with $N(u) \neq N(v)$ are not strongly fixed, and let $i$ be
        such that $b:=N(u)_i > N(v)_{\lfloor i\cdot m/n\rfloor}=:a$.
        Assuming there exists vertices $m$ in between $a$ and $b$, $l$ left of $\min
        N(v)$ and $r$ right of $\max N(u)$ \ragnar{Is this strong enough? Do $u$ and $v$
          need reversing? Or should we just say left of the min and right of the max
          of the two?}, there exists some \emph{weighted} distribution $X$ over
        $\{l, m, r\}$ such that $c(v, X, u) < \min(c(X, u, v), c(u, v, X))$, so that
        $v$ may have to go before $u$.

        \centering
        \includegraphics[scale=1.5]{fig/strongly-fixed.pdf}

@@

        \centering
        \includegraphics[scale=2]{fig/blocking-set.pdf}
    \end{column}

@@

        \begin{center}
          \vspace{-2em}
        \includegraphics[scale=2]{fig/gluing.pdf}
        \end{center}

@@

      \begin{block}{Performance}
        \textbf{Parameterized track:} All 200 instances in \textbf{10.37s} total
        time (second place).

        \textbf{Exact track:} 157/200 instanes.
